---
title: "Quicksort performance analysis"
author: "Ilya Meignan--Masson and Nour El hassane"
date: "2022-11-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
get_hostname <- function(){
  return(gsub(" ", "", as.character(Sys.info()["nodename"])))
}
```
# Problem statement
Improve the experimental design and the performance evaluation of a simple parallel quicksort implementation. This would be done by taking into accout the replication and randomization concepts, so that we have reliable unbiaised evaluations.

# Experimental design

## Generate the arrays of parameters (number of execution repetitions and different array sizes)
```{r}
#replication
number_of_repetitions <- c(0:10) 
sizes <- c("100","500", "1000","5000", "10000","50000", "100000")
```
## Generate the combinations
```{r}
#randomization
experiments <- crossing(number_of_repetitions, sizes)
experiments <- experiments[sample(1:nrow(experiments)), ]
experiments
```
## Run the functions
```{r}
# store the experiments parameters in a csv file
write.csv(experiments, "../data/nour_2022-11-23/experiments.csv", row.names=FALSE)
```


# Analysis of the results

```{r}
data <- read.csv(file=paste("data/nour_2022-11-23",paste(get_hostname(),"/measurements.txt", sep=""), sep=""))
```